%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%SURYA RESUME INSTRUCTIONS:
% 1. Install MikTex on your PC and open the Document using TexWorks
% 2. Open MikTex Console on your PC and go to packages and install fontawesome and fontawesome5
% 3. Try to compile the document using LuaLaTeX or XeLaTeX (LuaLaTeX Works properly with fontawesome)
%UPDATE
% 1. TexStudio is better than MikTex. Use TexStudio and compile with LuaLatex directly. No need to install package externally.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{surya-resume}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Surya Kiran}{Suresh}{ \urlstyle{same} \href{https://skiran13.github.io/}{skiran13.github.io} | \faGithub \href{https://github.com/skiran13}{ Github}\\
\faEnvelope[regular]\href{mailto:skiran13@gmail.com}{ skiran13@gmail.com} | \faMobile* { +91 8939593339}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{SRM Institute of}
\subsection{Science and Technology}
\descript{B. Tech in Computer}
\descript{Science and Engineering}
\location{2017 - 2021 (Ongoing)}
\location{\faMapMarker*{ Chennai, Tamil Nadu, IN}}
\sectionsep

\subsection{National Defence Academy}
\descript{Bachelor of Computer Science}
Tri-Services Training Academy \\
\location{2016 - 2017 (Dropped) \\ \faMapMarker*{ Pune, Maharashtra, IN}}
\sectionsep

\subsection{Maharishi Vidya Mandir}
\descript{11th \&\ 12th Grade}
\location{2014 - 2016 \\\faMapMarker*{ Chennai, Tamil Nadu, IN}}
\sectionsep

\subsection{Kendriya Vidyalaya}
\descript{10th Grade}
\location{2013 - 2014 \\\faMapMarker*{ Chennai, Tamil Nadu, IN}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\faGithub { Github}:// \href{https://github.com/skiran13}{\bf skiran13} \\
\faLinkedin { LinkedIn}://  \href{https://www.linkedin.com/in/surya-kiran-suresh-569548166/}{\bf Surya Kiran} \\
\faTwitter { Twitter}://  \href{https://twitter.com/skiran13}{\bf @skiran13} \\
\faQuora { Quora}://  \href{https://www.quora.com/profile/Surya-Kiran-34}{\bf Surya Kiran} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Coursework}
%
%\subsection{Undergraduate}
%Information Retrieval \\
%Operating Systems \\
%Artificial Intelligence + Practicum \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
%Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
\begin{tabular}{lll}
\textbullet{} Python &\textbullet{} NodeJS &\textbullet{} ReactJS\\
\textbullet{} Java &\textbullet{} C &\textbullet{} C++\\
\textbullet{} HTML &\textbullet{} Javascript &\textbullet{} Matlab\\
\end{tabular}

\sectionsep
\location{Over 1000 lines:}
\begin{tabular}{lll}
\textbullet{} Latex &\textbullet{} Markdown &\textbullet{} MySQL\\
\textbullet{} Assembly &\textbullet{} Sikuli \\
\end{tabular}

\sectionsep
\location{JS Frameworks}
\begin{tabular}{lll}
\textbullet{} Nodejs &\textbullet{} Reactjs &\textbullet{} Webpack \\
\textbullet{} Babel &\textbullet{} Parcel \\
\end{tabular}\\
\sectionsep
\location{UI Frameworks}
\begin{tabular}{lll}
\textbullet{} Semantic-ui &\textbullet{} Bulma-css &\textbullet{} Ant-d\\
\end{tabular}
\sectionsep
\subsection{Spoken Languages}
\begin{tabular}{lll}
\textbullet{} English &\textbullet{} Hindi &\textbullet{} Tamil
\end{tabular}
\sectionsep
\subsection{Interests}
\begin{tabular}{lll}
\textbullet{} Singing&\textbullet{} Piano&\textbullet{} Photography
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\location{An amateur full-stack web-developer interested in learning about emerging technologies and strives
to evolve. Well known for meticulous work, effecient time management and leardership skills.
Currently learning machine learning, artificial intelligence and neural networks. My code and contributions
can be viewed on my \faGithub \href{https://skiran13.github.io/}{ GitHub.}}
\sectionsep

\section{Experience}
\runsubsection{Crio.do}
\descript{| Student Developer}
\location{Jun 2019 | Chennai, Tamil Nadu, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed scalable distributed backend for Qeats Restaurants app
\item Distributed-backend developer - Wrote and reviewed code for Java implementing MVC and integrating MongoDB, RabbitMQ, Docker and Redis.
\item Performed Load testing using Jmeter and optimized the results using multithreading.
\end{tightemize}
\sectionsep
\runsubsection{AT \&\ T Aspire}
\descript{| Student Intern }
\location{Jan 2019 - Apr 2019 | Chennai, Tamil Nadu, IN}
\begin{tightemize}
\item Learnt and understood implementation of Natural Language Processing in Real Life Products.
\item Learnt how to create an Alexa Skill using Amazon Web Services.
\end{tightemize}
\sectionsep
\runsubsection{Design Esthetics}
\descript{| Software Engineering Intern }
\location{Dec 2018 | Bengaluru, Karnataka, IN}
\begin{tightemize}
\item Developed an online e-learning platform based on competitive examinations.
\item Full-stack developer - Wrote and reviewed code for JS using Node, React and MongoDB 
\end{tightemize}
\sectionsep
\runsubsection{SRM CARE}
\descript{| Software Engineering Intern }
\location{Jan 2018 - Present | Chennai, Tamil Nadu, IN}
\begin{tightemize}
\item Developed and deployed an online e-learning platform with a userbase of 10000+ students.
\item Full-stack developer - Wrote and reviewed code for JS using Node, React and MongoDB 
\item Making progressive web-apps to bolster the efficiency of work done in the college 
\end{tightemize}

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2019	     & 2\textsuperscript{nd}  & Overall Profecieny and Academics, SRMIST\\
2019	     & 1\textsuperscript{st}  & Hack it up v2, SRMIST\\    
2019	     & Student Coordinator  & Technozarre'19, SRMIST\\    
2018	     & 1\textsuperscript{st}  & Overall Profecieny and Academics, SRMIST\\
2018	     & 3\textsuperscript{rd}  & Hack it up, SRMIST\\
2018	     & Participation  & Data Science with Python Workshop, SRMIST\\    
2018	     & Participation  & Blockchain and Cryptocurrency, SRMIST\\    
2018	     & 1\textsuperscript{st}  & Geek of the Semester, SRMIST\\
2017	     & 2\textsuperscript{nd}  & Western Singing, SRMIST\\
2017	     & Participation  & Ubercode, SRMIST\\    
2016     & top 300/5Lakh & Service Selection Board Interview - Indian Navy  \\
2016     & top 350/10k & Service Selection Board Interview - Indian Army  \\
2016	     & top 10k/5Lakh  & UPSC - National Defence Academy \&\ Naval Academy\\
\end{tabular}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		NEW PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{1\textwidth} 

\section{Positions of Responsibility}
\runsubsection{Office Bearer}
\descript{| White Hat Hackers Club}
\location{Aug 2019 - Current | Chennai, Tamil Nadu, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working as an active Office Bearer of White Hat Hackers Club of SRM Vadapalani.
\end{tightemize}
\sectionsep

\runsubsection{Event Organizer}
\descript{| Ubertech 19}
\location{Aug 2019 | Chennai, Tamil Nadu, IN}
\begin{tightemize}
\item Organized Data Analytics workshop for National Technical Symposium Ubertech in SRM Vadapalani.
\end{tightemize}
\sectionsep

\runsubsection{Student Coordinator}
\descript{| Technozarre 19}
\location{Feb 2019 | Chennai, Tamil Nadu, IN}
\begin{tightemize}
\item Worked as a Student Coordinator for National Technical Symposium Technozarre in SRM Vadapalani.
\end{tightemize}
\sectionsep
\runsubsection{Cadet}
\descript{| National Defence Academy}
\location{Jan 2017 - Mar 2017 | Pune, Maharashtra, IN}
\begin{tightemize}
\item Served as an Officer Cadet in the Indian Army (Batch 137)
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Stock Price Prediction}
\descript{| Python}
\location{Sep 2019 | Chennai, Tamil Nadu, IN}
A machine learning model used to Predict stock prices using different indicators as input and predicting using LSTM.
\sectionsep

%\runsubsection{WHHC Landing Page}
%\descript{| ReactJS}
%\location{Sep 2019 | Chennai, Tamil Nadu, IN}
%A web app which serves as a landing page for White Hat Hackers Club of SRM Vadapalani Campus.
%\sectionsep

\runsubsection{SMS Spam Filter}
\descript{| Python}
\location{Aug 2019 | Chennai, Tamil Nadu, IN}
A machine learning model used to classify text messages as Spam or Not Spam using Natuaral Language Processing.
\sectionsep

\runsubsection{Traffic Volume Prediction}
\descript{| Python}
\location{Aug 2019 | Chennai, Tamil Nadu, IN}
A machine learning model used to Predict traffic volume in a particular area at any given point of time using Gradient Boosted Trees.
\sectionsep

\runsubsection{Automatic Licence Plate Recognition}
\descript{| Python}
\location{Mar 2019 | Chennai, Tamil Nadu, IN}
A machine learning model used to detect Licence plate and extract the Licence plate number from cctv footages built using darkflow and yolov2.
\sectionsep

\runsubsection{eCircuit}
\descript{| ReactJs | NodeJs}
\location{Jan 2019 - Current | Chennai, Tamil Nadu, IN}
An online laboratory platform to make the students of Electrical and Electronics based departments perform different experiments on an applet through a computer.\sectionsep

\runsubsection{ExamAdda}
\descript{| ReactJs | NodeJs}
\location{Dec 2018 | Bengaluru, Karnataka, IN}
An online self evaluation tool to help students prepare for all sorts competitive examinations in different sectors.
\sectionsep

\runsubsection{eSkill}
\descript{| ReactJs | NodeJs}
\location{May 2018 - Dec 2018 | Chennai, Tamil Nadu, IN}
An online self evaluation tool to help students prepare for competitive examinations like GRE, GMAT etc.
\sectionsep

\runsubsection{eApproval}
\descript{| ReactJs | NodeJs}
\location{Dec 2017 - May 2018 | Chennai, Tamil Nadu, IN}
An online platform to ease the administration and workflow of approving all different kinds of applications in SRMIST by automating the reduntant processes. 
\sectionsep

\runsubsection{eLab Printer}
\descript{| Python}
\location{Sep 2017 | Chennai, Tamil Nadu, IN}
A Python application made using Selenium Scripting for automation of lab record printing from eLab for students of SRMIST.
\sectionsep

\runsubsection{Online Quiz}
\descript{| C++}
\location{Jan 2016 – March 2016 | Chennai, Tamil Nadu, IN}
An Online Quiz application built using basic C++ libraries.
\end{minipage}

\end{document}  \documentclass[]{article}
